Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-07-19 paper.tex
Jessie and Lee's comments

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy levels and schematic of Raman sideband cooling.
    The Raman transitions have a one photon detuning $\Delta=25$ GHz from the D2 line.
    We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
    state to minimize heating on the atom in the $|F=2,m_F=-2\rangle$ state
    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
    optical tweezer and bias magnetic field.
    (C) Schematic of the cooling sequence. The tweezer switches at 3 MHz to
    reduce light shifts during optical pumping. Each cooling cycle consists of $8$ pulses.
    The four axial pulses are addressing two neighboring cooling orders.
    The two pulses in each radial directions are either addressing two neighboring cooling orders
    or having different length on the first order when most of the population are below $n=3$
    towards then end of the cooling sequence.
    All of the Raman pulses use Blackman pulse envelopes to reduce the off resonance
    coupling to carrier and heating sidebands.
    \label{f-setup}}
\end{figure*}
\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Optical pumping state changing probability and Raman matrix element for axial direction.
    The range plotted covers $95$\% of the initial thermal distribution.
    (A) Axial motional state distribution after one optical pumping cycle
    for different initial $n$. Due to the large Lamb-Dicke parameter,
    there is a high probability of $n$ changing.
    (B) Matrix elements for Raman transition in the axial direction showing deviation from
    $\sqrt{n}$ scaling and multiple minima for different sideband orders.
    ($k$ is the difference in wave vector of the Raman beams,
    $r$ is the coordinate in axial direction).
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{(A) Radial Raman sideband spectrum of first order heating, first order cooling and
    second order cooling before and after Raman sideband cooling.
    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband
    before (red) and after (blue) cooling.
    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
    The blue lines corresponds to a ground state probability of $93$\% after cooling and
    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{(A) Axial Raman sideband spectrum from first order heating to eighth order cooling
    before and after Raman sideband cooling.
    The data for the second and higher orders of cooling sidebands are taken with 150 $\mu$s
    pulse time and the rest are taken with 125 $\mu$s pulse time.
    (B,C) Rabi flopping on axial (B) carrier and (C) first order heating sideband
    before (red) and after (blue) cooling.
    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
    The blue and green lines corresponds to a ground state probability of $92$\% after cooling and
    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
    The blue lines do not take into account the effect of decoherence due to resonance
    fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,
    we can clearly see that this effect is the strongest for the after cooling data on
    the axial heating sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

It is important that the re-pumping step scatter as few photons as possible to minimize heating.  Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line since the $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}.  Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=r, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.

For an atom in motional level $n$, the OP could result in motional-state redistribution
as shown in Fig.~\ref{f-ld}A. The state redistribution probability
is approximately proportional to the effective LD parameter
$\eta^{OP}_{\eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
$k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
$m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
Such heating presents a major challenge for efficient cooling of single Na atoms
which feature a light mass and short D-line wavelengths.
For our trap frequencies and beam geometry,
$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$.
Combined with a relatively large PGC temperature gives initial
$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$.
For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the LD regime.
As a result, the average change of motional state per OP step is large,
which creates a large uncertainty on the motional state at the end of a full RSC step, and possibly leading to runaway heating.
For example, the average change in motional states over the initial distribution
is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.

Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
The Raman transitions in our configuration have
$\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
which allow strong coupling to higher order sidebands for atoms in large motional states
as calculated in Figure~\ref{f-ld}B.
To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
to remove more motional quanta in a single cooling pulse.
Since the coupling strengths of different orders do not reach minima for the same pulse duration,
using multiple orders of cooling sidebands avoids accumulations of population
near the coupling minima.

@@

There are two additional important challenges in cooling single sodium atoms.
First, the high initial temperature populates high motional states,
meaning that the atoms sample the anharmonicity of the trap away from the center.
In order to address this, we drive the sidebands with a large Rabi frequency
and short pulses to Fourier broaden the spectrum coverage, and use Blackman pulse envelopes
to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a
Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
Second, the tweezer trap causes a large AC Stark shift (as large as $300$ MHz)
in the excited state. This creates a large, position-dependent OP detuning
and mixes the excited-state hyperfine levels, which reduces the optical pumping fidelity.
We address this by switching the trapping light at 3 MHz during the whole cooling sequence,
similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
while leaving OP on with constant intensity.
Due to the large light shift, the optical pumping is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied along three axes with
cooling beginning on the radial second order.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry.
For the more tightly confined (non-degenerate) radial directions,
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
It is important to note that the simple sideband thermometry formula,
which predicts the ratio of the cooling and heating sideband heights
to be $\bar n / (\bar n + 1)$~\cite{Monroe1995},
assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
However, outside of the LD regime, the coupling strength deviates from this simple scaling rule rapidly,
as shown in figure \ref{f-ld}A.  Since the Raman spectroscopy is performed
with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to
measure $\bar n$.
Instead, given the absence of the second order cooling sideband,
we assume \fxnote{[What is the cutoff for the validity of this assumption, and are we below that cutoff?]} that the atoms are cold enough to have stronger coupling to the first order cooling
sideband than the second order, in which case the lower bound of the ground state population
can be computed from the heights of the sidebands by assuming all of the excitation are in the
$n=1$ state. In doing this, we found a ground state population of $90(2)$\%
and $94(3)$\% along the two radial directions.
We also use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)$\% and $92(2)$\% and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping to obtain the initial temperature of $70 \mu$K.

For the weaker axial direction, cooling is much more challenging
due to the large $\eta^{OP}_{eff1}\approx 4.0(2)$.
We observe up to 8th-order Raman cooling sidebands initially,
which indicates population in highly-excited motional states.
Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are suppressed
after RSC (Fig.~\ref{f-axial}).
The ground state probability calculated using the ratio of first-order sideband heights yields
$92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
and extracted a ground state population of $91(2)$\%, in agreement with the other method.
For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
we observed additional decoherence that is more produced due to the slower Rabi frequency.
The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG
that we measure independently in the lab, which produces a Zeeman shift of $\sim 3$ kHz.

@@

There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss from very high-lying initial motional states
that are not efficiently cooled by RSC, but off-resonantly heated by the Raman beams.  These give us a $66(3)$\% probability of ground state atom after each successful loading event.
We are planning to improve these by increasing the detuning of the Raman beams,
addressing wider range of trap anharmonicity by frequency sweeps,
implementing better control of the magnetic field, and optimizing the temperature during imaging.
Another improvement could be to implement grey molasses cooling to achieve
a lower starting temperature before RSC\cite{Colzi2016}.

@@

>>>>

\begin{figure*}
  \includegraphics[height=5.2cm]{imgs/Na_RSC_schematic.pdf}
  \includegraphics[height=4.5cm]{sequence.pdf}
  \caption{(A) Energy levels and schematic of Raman sideband cooling.
    The Raman transitions have a one photon detuning $\Delta=25$ GHz from the D2 line.
    We use D1 light with $\sigma^-$ polarization to repump atoms out of $|F=2,m_F=-1\rangle$
    state to minimize heating on the atom in the $|F=2,m_F=-2\rangle$ state
    (B) Geometry and polarizations of the Raman and optical pumping beams relative to the
    optical tweezer and bias magnetic field.
    (C) Schematic of the cooling sequence. The tweezer switches at 3 MHz to
    reduce light shifts during optical pumping. Each cooling cycle consists of $8$ pulses.
    The four axial pulses are addressing two neighboring cooling orders.
    The two pulses in each radial direction are either addressing two neighboring cooling orders
    or having different length on the first order when most of the population are below $n=3$
    towards the end of the cooling sequence.
    All of the Raman pulses use Blackman pulse envelopes to reduce the off-resonant
    coupling to carrier and heating sidebands.
    \label{f-setup}}
\end{figure*}
\begin{figure}[b]
  \includegraphics[width=8.5cm]{imgs/fig2_raman_op.pdf}
  \caption{Optical pumping state changing probability and Raman matrix element for axial direction.
    The range plotted covers $95$\% of the initial thermal distribution.
    (A) Axial motional state distribution after one optical pumping cycle
    for different initial $n$. Due to the large Lamb-Dicke parameter,
    there is a high probability of $n$ changing.
    (B) Matrix elements for Raman transition in the axial direction showing deviation from
    $\sqrt{n}$ scaling and multiple minima for different sideband orders.
    ($k$ is the difference in wave vector of the Raman beams,
    $r$ is the coordinate in axial direction).
    \label{f-ld}}
\end{figure}
\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_r.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_r3_p1.pdf}
  \caption{(A) Radial Raman sideband spectrum of first order heating, first order cooling and
    second order cooling before and after Raman sideband cooling.
    (B,C) Rabi flopping on axis 3 (B) carrier and (C) first order heating sideband
    before (red) and after (blue) cooling.
    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
    The blue lines correspond to a ground state probability of $93$\% after cooling and
    the red lines correspond to a thermal distribution of $70$ $\mu$K before cooling.
    \label{f-radial}}
\end{figure*}
\begin{figure*}
  \includegraphics[height=4.2cm]{imgs/spectrum_a1.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_0.pdf}
  \includegraphics[height=4.2cm]{imgs/rabi_flop_a1_p1.pdf}
  \caption{(A) Axial Raman sideband spectrum from first order heating to eighth order cooling
    before and after Raman sideband cooling.
    The data for the second and higher orders of cooling sidebands are taken with 150 $\mu$s
    pulse time and the rest are taken with 125 $\mu$s pulse time.
    (B,C) Rabi flopping on axial (B) carrier and (C) first order heating sideband
    before (red) and after (blue) cooling.
    Solid lines in (B) and (C) are theoretical calculation of the Rabi flopping.
    The blue and green lines corresponds to a ground state probability of $92$\% after cooling and
    the red lines corresponds to a thermal distribution of $70$ $\mu$K before cooling.
    The blue lines do not take into account the effect of decoherence due to resonance
    fluctuation. By comparing it to the green line in (C), which includes a $3$ kHz fluctuation,
    we can clearly see that this effect is the strongest for the post-cooling data on
    the axial heating sideband where the Rabi frequency is the lowest.
    \label{f-axial}}
\end{figure*}

@@

It is important that the re-pumping step scatter as few photons as possible to minimize heating.  Therefore, we use a $\sigma^-$-polarized laser resonant with the D1 line since the $|F=2, m_F=-2\rangle$ is a dark state in this case \fxnote{cite ion and K39}. Compared to using a D2 repump beam, from which the $|F=2, m_F=-2\rangle$ state could always scatter a photon via the excited $|F=3, m_F=-3\rangle$ state, we find a reduction in the scattering rate of a factor of $130(20)$.

For an atom in motional level $n$, the OP could result in motional-state redistribution
as shown in Fig.~\ref{f-ld}A. The state redistribution probability
is approximately proportional to the effective LD parameter
$\eta^{OP}_{eff}=\sqrt{2n+1}\eta^{OP}$, where $\eta^{OP}=k z_0=k \sqrt{\hbar/2m\omega}$,
$k$ is the wavenumber of the optical pumping beam, $z_0$ is the zero-point wavefunction spread,
$m$ is the mass of the atom, and $\hbar$ is the reduced Planck constant.
Such heating presents a major challenge for efficient cooling of single Na atoms
which feature a light mass and short D-line wavelengths.
For our trap frequencies and beam geometry,
$\{\eta^{OP}_1,\eta^{OP}_2,\eta^{OP}_3\} = \{0.602(5), 0.241(2), 0.206(1)\}$.
Combined with a relatively large PGC temperature gives initial
$\{\eta^{OP}_{1\eff},\eta^{OP}_{2\eff},\eta^{OP}_{3\eff}\} = \{4.0(1), 0.67(2), 0.50(1)\}$.
For the weak axial direction, $(\eta^{OP}_{1\eff})^2>1$ is far outside of the LD regime.
As a result, the average change of motional state per OP step is large,
which creates a large uncertainty on the motional state at the end of a full RSC step, possibly leading to runaway heating.
For example, the average change in motional states over the initial distribution
is $2.4$ in the axial direction, which is significantly greater than $0.89-0.95$
in previous experiments of RSC of Rb and Cs~\cite{Li2012,Kaufman2012,Thompson2013,Liu2017}.

Fortunately, the large LD parameters also provide opportunities to overcome OP heating.
The Raman transitions in our configuration have
$\{\eta^R_{1},\eta^R_{2},\eta^R_{3}\} = \{0.40(1), 0.341(2), 0.291(1)\}$,
which allow strong coupling to higher order sidebands for atoms in higher motional states
as calculated in Figure~\ref{f-ld}B.
To offset heating from OP initially, higher-order Raman cooling sidebands can be utilized
to remove more motional quanta in a single cooling pulse.
Since the coupling strengths of different orders do not reach minima for the same pulse duration,
using multiple orders of cooling sidebands avoids accumulations of population
near the coupling minima.

@@

There are two additional important challenges in cooling single sodium atoms.
First, the high initial temperature populates high motional states,
meaning that the atoms sample the anharmonicity of the trap away from the center.
In order to address this, we drive the sidebands with a large Rabi frequency
and short pulses to Fourier broaden the spectrum coverage, and use Blackman pulse envelopes
to avoid unwanted coupling to the carrier and heating sidebands~\cite{Kasevich1992}.
The anharmonicity in the radial directions is calculated to be 1kHz/n, meaning that a
Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
Second, the tweezer trap causes a large AC Stark shift (as large as $300$ MHz)
in the excited state. This creates a large, position-dependent OP detuning
and mixes the excited-state hyperfine levels, which reduces the optical pumping fidelity.
We address this by switching the trapping light at 3 MHz during the whole cooling sequence,
similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
while leaving OP on with constant intensity.
Due to the large light shift, the OP is effectively off whenever the trap light switches back on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shifts on OP fidelity is suppressed.

Our final cooling results are shown in Fig.~\ref{f-radial} and \ref{f-axial}.
In total, $1000$ cooling pulses (with a total duration of $100$ ms) are applied along three axes with
cooling beginning on the radial second order.
To characterize the single atom thermal occupation before and after cooling,
we perform Raman sideband thermometry.
For the more tightly confined (non-degenerate) radial directions,
we observe clear first-order heating, first-order cooling,
and second-order cooling sidebands before RSC as is shown in red in Figure \ref{f-radial}A.
After cooling, the first and second order cooling sidebands on both radial axes are suppressed.
It is important to note that the simple sideband thermometry formula,
which predicts the ratio of the cooling and heating sideband heights
to be $\bar n / (\bar n + 1)$~\cite{Monroe1995},
assumes that the coupling strength for different motional states to be proportional to $\sqrt{n}$.
However, outside of the LD regime,
the coupling strength rapidly deviates from this simple scaling rule,
as shown in figure \ref{f-ld}A.  Since the Raman spectroscopy is performed
with relatively large Raman LD parameters $\eta^R$, we cannot use this formula to
measure $\bar n$.
Instead, given the absence of the second order cooling sideband,
we assume \fxnote{[What is the cutoff for the validity of this assumption, and are we below that cutoff?]} that the atoms are cold enough to have stronger coupling to the first order cooling
sideband than the second order, in which case the lower bound of the ground state population
can be computed from the heights of the sidebands by assuming all of the excitations are in the
$n=1$ state. In doing this, we found a ground state population of $90(2)$\%
and $94(3)$\% along the two radial directions.
We also use an independent measurement of Rabi flopping on the carrier (Fig. \ref{f-radial}B)
and first-order heating(Fig. \ref{f-radial}C) sidebands
to verify the ground state population~\cite{Meekhof1996}.
The data is fitted using the same Monte-Carlo simulation we used to simulate the cooling
which yields $89(2)$\% and $92(2)$\% and show good agreement with
the population extracted from the sideband thermometry.
We also extracted the initial temperature before cooling
from the motional-state decohered Rabi flopping to obtain the initial temperature of $70 \mu$K.

For the weaker axial direction, cooling is much more challenging
due to the large $\eta^{OP}_{1eff}\approx 4.0(2)$.
We observe up to 8th-order Raman cooling sidebands initially,
which indicates population in highly-excited motional states.
Nevertheless, our cooling sequence works efficiently as all the cooling sidebands are suppressed
after RSC (Fig.~\ref{f-axial}).
The ground state population calculated using the ratio of first-order sideband heights yields
$92(3)$\%. We also perform Rabi flopping on the carrier(Figure~\ref{f-axial}B)
and extracted a ground state population of $91(2)$\%, in agreement with the other method.
For the first-order heating sideband Rabi flopping (Figure~\ref{f-axial}C),
we observed additional decoherence that is more pronounced due to the slower Rabi frequency.
The decoherence time scale is consistent with magnetic field fluctuations of $1.5$ mG
that we measure independently in the lab, which produces a Zeeman shift of $\sim 3$ kHz.

@@

There is an additional $5$\% loss from finite imaging fidelity and $10$\% loss
from very high-lying initial motional states that are not efficiently cooled by RSC,
but instead off-resonantly heated by the Raman beams.
These give us a $66(3)$\% probability of ground state atom after each successful loading event.
We are planning to improve these by increasing the detuning of the Raman beams,
addressing a wider range of trap anharmonicity by frequency sweeps,
implementing better control of the magnetic field, and optimizing the temperature during imaging.
Another improvement could be to implement grey molasses cooling to achieve
a lower starting temperature before RSC\cite{Colzi2016}.

@@

% Define \eta_R
% Lamb-Dicke parameter square explain
% why not just molecules instead of polar molecules
% entropy
% use different line shape for rabi flopping
% mention axis definitions
% heating from trap -> decrease of ground state procetage (maybe add temprature too)
% Differetial AC starck shift **between excited states and ground states**?
% at the same time, the atom is cooled via PGC instead of "the same imaging light is used to"
% 1 sentence to explain why anisotropy?
% is strobed at 3MHz instead of is switching at...
% Cite Na loading paper in caption?
% Make sure the caption for the before cooling axial rabi flopping mentions decoherence
% Mention after cooling is non-thermal?
% Make it clear that we cool for 6-15 cycles each time before going to the next set of orders in axial

% sm:
% mention the simulation results are 3d
% effect of changing groups.
% mention effects that are included first.

### 2017-07-19 sm.tex
Jessie and Lee's comments

%\subsection{Overview}

We use a computer simulation to study the importance of different effects
and guide the optimization of Raman sideband cooling.
The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Chretien2014} 
to accurately calculate the evolution within each laser pulse where different energy eigenstates
are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
Such approximations are valid and greatly simplifies the computation
at the cost of limiting the applicability of the simulation to processes that requires stronger
coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap.

@@

%\subsection{Simulation of each pulse}

In general, each pulse has a coherent part from the Raman drive (which is absent for the optical pumping pulses)
and an incoherent part from scattering (optical pumping or off-resonant).
This nicely fits the general approach of the quantum jump method. Due to the large number of
states that we need to take into account ($30-150$ motional per axis and
$8$ hyperfine, giving a total of $10^6$),
 generic wavefunction propagation is very inefficient.
Therefore, we further simplify by reducing the number of states tracked during
the coherent propagation and apply quantum jumps using a set of reduced jump operator that
describes the total jump probability from a certain states (summed over all final states).
The coherent propagation is then accurately solved in order to avoid having to use a time step
much shorter than the scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.

In order to simulate a pulse, we first start with the coherent propagation that includes the
modification from the jump operators as in quantum jump method.
When a jump happens, we pick a final internal state to jump to based on the relative rates
of different scattering sources and their branching ratios.
This process also determines the polarization and emission pattern of the photon and
a particular wave vector for the emitted photon is then selected as the next step.
The recoil is now fixed so the final motional state of the atom can now be selected.
This process is then repeated on the same pulse until the pulse time is used up before
we start to simulate the next pulse.

%\subsection{Measurements}

@@

%\subsection{Code}

>>>>

We use a computer simulation to study the importance of different effects
and guide the optimization of Raman sideband cooling.
The simulation uses the quantum jump (or Monte-Carlo wavefunction) method~\cite{Chretien2014}
to accurately calculate the evolution within each laser pulse where different energy eigenstates
are assumed to decohere immediately upon spontaneous emission and on pulse boundaries.
Such approximations are valid and greatly simplify the computation
at the cost of limiting the applicability of the simulation to processes that require stronger
coherence, such as Ramsey spectroscopy or rapid push-out of the atoms from the trap
(faster than a trap oscillation period).

@@

In general, each pulse has a coherent part from the Raman drive
(which is absent for the optical pumping pulses)
and an incoherent part from scattering (optical pumping or off-resonant).
This nicely fits the general approach of the quantum jump method.
Due to the large number of states that we need to take into account
($30-150$ motional per axis and $8$ hyperfine, giving a total of $10^6$),
generic wavefunction propagation is very inefficient.
Therefore, we further simplify by reducing the number of states tracked during
the coherent propagation and applying quantum jumps using a set of reduced jump operators that
describe the total jump probability from a certain state (summed over all final states).
The coherent propagation is then accurately solved in order to avoid having to use a time step
much shorter than the inverse of scattering rate (up to hundreds of kHz)\footnote{\href{https://goo.gl/EZ13wt}{note about modification to the quantum jump method (https://goo.gl/EZ13wt)}}.

In order to simulate a pulse, we first start with the coherent propagation that includes the
modification from the jump operators as in the quantum jump method.
When a jump happens, we pick a final internal state to jump to based on the relative rates
of different scattering sources and their branching ratios.
This process determines the polarization and emission pattern of the emitted photon,
from which we randomly sample a particular wave vector.
The photon recoil being defined, we can then assign a final motional state to the atom.
This process is then repeated as long as the pulse is on,
before we start to simulate the next pulse.

@@
